Interactive dashboard to monitor the COVID-19 outbreak and Vaccine Administration

### 2022-05-08 manuscript_covid19dashboard.Rmd
Completed introduction

COVID-19 has expanded over the globe, having a significant impact on our daily lives and work. In the fight against COVID-19, early responses and timely decisions and actions are critical to save communities and economy worldwide. In order to make effective decisions, data is essential. Data-driven information guide the decision-making process and also evaluate the effectiveness of strategies taken.

In the response to the COVID-19 pandemic, massive amounts of data are being generated. Given such available data, it is critical to create tools for exploratory analysis for policy makers, health officials, and the general public. Dashboards are one of the greatest visual interpretation methods for tracking the COVID-19 pandemics spread and vaccine administration. Dashboards allow user to quickly interact with combination of exploratory visualizations and gain quick overview of the data. This paper describes the development and implementation of dashboard for COVID-19 outbreak and vaccine administration data  in Sri Lanka.

There are a plethora of COVID-19 visualization dashboards that have been designed to visualize the pandemic's global and local status. Different software can be used to generate dashboards. We explored 15 dashboards designed to visualize COVID-19 data in the global and country levels. First, dashboards were compared to identify the various features, visualization approaches, and enhancements that should be implemented. Next, we developed an interactive dashboard to visualized COVID-19 outbreak and vaccination information in Sri Lanka. This dashboard provides front-line health officers a situational awareness of spread of COVID-19 and status of the vaccination program.

The rest of the paper is organized as follows: the [Section 2](#litreview) of dashboards created using data related to COVID-19 pandemic. [Section 3](#methods) provides the methodology and basic design concept; [Section 4](#results) presents results; and [Section 5](#conclusion) offers some concluding remarks.

>>>>

COVID-19 has expanded over the globe, having a significant impact on our daily lives and work. Early responses and timely decisions and actions are critical to saving communities and economy worldwide. Data is essential in order to make effective decisions. Data-driven information guides the decision-making process and also evaluates the effectiveness of strategies taken.

Massive amounts of data are being generated in the response to the COVID-19 pandemic. Given this available data, it is critical to create tools for exploratory analysis for policymakers, health officials, and the general public. Dashboards are one of the greatest visual interpretation methods for tracking the COVID-19 pandemic's spread and vaccine administration. Dashboards allow users to quickly interact with a combination of exploratory visualizations and gain a quick overview of the data. This paper describes the development and implementation of a dashboard for the COVID-19 outbreak and vaccine administration data in Sri Lanka.

There are a plethora of COVID-19 visualization dashboards that have been designed to visualize the pandemic's global and local status. Different software can be used to generate dashboards. We explored 15 dashboards designed to visualize COVID-19 data at the global and country levels. First, dashboards were compared to identify the various features, visualization approaches, and enhancements that should be implemented. Next, we developed an interactive dashboard to visualize the COVID-19 outbreak and vaccination information in Sri Lanka. This dashboard provides front-line health officers a situational awareness of the spread of COVID-19 and status of the vaccination program.

The rest of the paper is organized as follows: [Section 2](#litreview) of dashboards created using data related to the COVID-19 pandemic. [Section 3](#methods) presents the methodology and basic design concept; [Section 4](#results) presents the results; and [Section 5](# conclusion) concludes.

### 2022-05-08 manuscript_covid19dashboard.tex
Completed introduction

COVID-19 has expanded over the globe, having a significant impact on our
daily lives and work. In the fight against COVID-19, early responses and
timely decisions and actions are critical to save communities and
economy worldwide. In order to make effective decisions, data is
essential. Data-driven information guide the decision-making process and
also evaluate the effectiveness of strategies taken.

In the response to the COVID-19 pandemic, massive amounts of data are
being generated. Given such available data, it is critical to create
tools for exploratory analysis for policy makers, health officials, and
the general public. Dashboards are one of the greatest visual
interpretation methods for tracking the COVID-19 pandemics spread and
vaccine administration. Dashboards allow user to quickly interact with
combination of exploratory visualizations and gain quick overview of the
data. This paper describes the development and implementation of
dashboard for COVID-19 outbreak and vaccine administration data in Sri
Lanka.

There are a plethora of COVID-19 visualization dashboards that have been
designed to visualize the pandemic's global and local status. Different
software can be used to generate dashboards. We explored 15 dashboards
designed to visualize COVID-19 data in the global and country levels.
First, dashboards were compared to identify the various features,
visualization approaches, and enhancements that should be implemented.
Next, we developed an interactive dashboard to visualized COVID-19
outbreak and vaccination information in Sri Lanka. This dashboard
provides front-line health officers a situational awareness of spread of
COVID-19 and status of the vaccination program.

The rest of the paper is organized as follows: the
\protect\hyperlink{litreview}{Section 2} of dashboards created using
data related to COVID-19 pandemic. \protect\hyperlink{methods}{Section
3} provides the methodology and basic design concept;
\protect\hyperlink{results}{Section 4} presents results; and
\protect\hyperlink{conclusion}{Section 5} offers some concluding
remarks.

>>>>

COVID-19 has expanded over the globe, having a significant impact on our
daily lives and work. Early responses and timely decisions and actions
are critical to saving communities and economy worldwide. Data is
essential in order to make effective decisions. Data-driven information
guides the decision-making process and also evaluates the effectiveness
of strategies taken.

Massive amounts of data are being generated in the response to the
COVID-19 pandemic. Given this available data, it is critical to create
tools for exploratory analysis for policymakers, health officials, and
the general public. Dashboards are one of the greatest visual
interpretation methods for tracking the COVID-19 pandemic's spread and
vaccine administration. Dashboards allow users to quickly interact with
a combination of exploratory visualizations and gain a quick overview of
the data. This paper describes the development and implementation of a
dashboard for the COVID-19 outbreak and vaccine administration data in
Sri Lanka.

There are a plethora of COVID-19 visualization dashboards that have been
designed to visualize the pandemic's global and local status. Different
software can be used to generate dashboards. We explored 15 dashboards
designed to visualize COVID-19 data at the global and country levels.
First, dashboards were compared to identify the various features,
visualization approaches, and enhancements that should be implemented.
Next, we developed an interactive dashboard to visualize the COVID-19
outbreak and vaccination information in Sri Lanka. This dashboard
provides front-line health officers a situational awareness of the
spread of COVID-19 and status of the vaccination program.

The rest of the paper is organized as follows:
\protect\hyperlink{litreview}{Section 2} of dashboards created using
data related to the COVID-19 pandemic.
\protect\hyperlink{methods}{Section 3} presents the methodology and
basic design concept; \protect\hyperlink{results}{Section 4} presents
the results; and \protect\hyperlink{ux5cux2520conclusion}{Section 5}
concludes.
